---
title: "GooglePlay"
author: "Belen_Miguel"
date: "18 de diciembre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
datos <- read.csv(file="googleplaystore.csv", header=TRUE, sep=",", stringsAsFactors = FALSE)

```

# Limpieza de datos y transformación
El primer paso será hacer un preprocesamiento de cada uno de los atributos con vista a obtener mejores resultados en los algoritmos de minería de datos

## Size
It can be seen that data has metric prefixes (Kilo and Mega) along with another string. Replacing k and M with their values to convert values to numeric.
- Replacing 'Varies with Device' by nan and
- Converting 1,000+ to 1000, to make it numeric
```{r}
print(head(datos$Size))
```


```{r}
for (i in 1:length(datos$Size)) { 
  if(grepl("M",datos$Size[i])){
    numero <- as.numeric(gsub("M", "e+06", datos$Size[i]))
    datos$Size[i]<- numero
  } else if (grepl("k", datos$Size[i])){
    numero <- as.numeric(gsub("k", "e+03", datos$Size[i]))
    datos$Size[i] <- numero
  }else if (grepl("Varies", datos$Size[i])){
    datos$Size[i] <- NaN
  }else{
    datos$Size[i]<-1000
  }
}

datos$Size <- as.numeric(datos$Size)

print(head(datos$Size))

```


```{r}

```


